Working title: Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-09-17 write_up/mixfishsim_ecolmod.tex
Text tweaks

Fishers exploit a variety of fish populations that are heterogeneously
distributed in space and time with varying knowledge of species distributions.
As fishers do not have full control over what species they select in `mixed
fisheries' this can result in catch of low quota or protected species. This
leads to discarding of over-quota catch if it is a species for which they have
no quota, limiting control over fishing mortality \citep{Alverson1994,
	Crowder1998, Rijnsdorp2007} and the ability to manage fisheries for the
biological and economic sustainability \citep{Ulrich2011a, Batsleer2015}.\\

There is increasing interest in technical solutions such as gear and spatial
closures as measures to reduce unwanted catch \citep{Kennelly2002,
	Catchpole2008, Bellido2011, Cosgrove2019} and adaptive spatial
management strategies have been proposed as a way of reducing over-quota
discards \citep{Holmes2011, Little2014, Dunn2014a}. However, if fisheries are
to reduce unwanted catch through spatial avoidance, an in-depth understanding
of spatiotemporal fishery dynamics is required. Implementation of spatial
measures is hampered by a lack of knowledge of fish and fishery spatiotemporal
dynamics and understanding of the scale at which these processes become
important for management. \\

Understanding the correct scale for spatial management measures to be effective
is also crucial as it enables implementation of effective solutions which
minimise economic impact \citep{Dunn2016}. For example, the problem can be to
identify a scale that promotes species avoidance for vulnerable or low quota
species while allowing continuance of sustainable fisheries for available quota
species. Identifying the correct spatial scale remains a challenge because data
on fish location at high temporal and spatial resolutions is expensive and
difficult to collect and proxies are usually inferred from scientific surveys
or commercial catches with limited spatial and temporal resolution. \\

@@

More refined spatiotemporal information has since become available through the
combination of logbook and Vessel Monitoring System (VMS) data \citep{Lee2010,
	Bastardie2010, Gerritsen2012, Mateo2016} and more real-time spatial
management has been possible \citep[e.g.][]{Holmes2011}.  However, fishers
establish favoured fishing grounds through an explore-exploit strategy
\citep{Rijnsdorp2011, Bailey2018} where they search for areas with high catches
and then use experience to return to areas where they've experienced high catch
in the past.  This leads to an inherently biased sampling where target species
are over-represented in the catch as fishers exploit areas of high abundance.
\\

To understand the effect of spatiotemporal aggregation of data and fishery
targeting on our understanding of fish communities we ask two fundamental
questions regarding inference derived from observational data:

\begin{enumerate}
	\item Do different source of sampling-derived fisheries data
		reflects the underlying community structure or represent a
		biased picture? 	
	\item How does data aggregation and data source impact on the success
		of spatial fisheries management measures?
\end{enumerate}

>>>>

Fishers exploit a variety of fish populations that are heterogeneously
distributed in space and time with varying knowledge of species distributions.
As fishers do not have full control over what species they select in `mixed
fisheries' this can result in catch of low quota or protected species. If
fishers discard over-quota catch of a species for which they have no quota, it
limits our ability to control fishing mortality \citep{Alverson1994,
	Crowder1998, Rijnsdorp2007} and the ability to manage fisheries for the
biological and economic sustainability \citep{Ulrich2011a, Batsleer2015}.\\

There is increasing interest in technical solutions such as gear and spatial
closures as measures to reduce unwanted catch \citep{Kennelly2002,
	Catchpole2008, Bellido2011, Cosgrove2019} and adaptive spatial
management strategies have been proposed as a way of reducing over-quota
discards \citep{Holmes2011, Little2014, Dunn2014a}. However, if fisheries are
to reduce unwanted catch through spatial avoidance, an in-depth understanding
of spatiotemporal fishery dynamics is required. \\

Understanding the correct scale for spatial management measures to be effective
is crucial as it enables implementation of effective solutions which minimise
economic impact \citep{Dunn2016}. For example, the problem can be to identify a
scale that promotes species avoidance for vulnerable or low quota species while
allowing continuance of sustainable fisheries for available quota species.
Identifying the correct spatial scale remains a challenge because data on fish
location at high temporal and spatial resolutions is expensive and difficult to
collect and proxies are usually inferred from scientific surveys or commercial
catches with limited spatial and temporal resolution. Thus, implementation of
spatial measures is hampered by a lack of knowledge of fish and fishery
spatiotemporal dynamics and understanding of the scale at which these processes
become important for management. \\ \\

@@

More refined spatiotemporal information has since become available through the
combination of logbook and Vessel Monitoring System (VMS) data \citep{Lee2010,
	Bastardie2010, Gerritsen2012, Mateo2016} and more real-time spatial
management has been possible \citep[e.g.][]{Holmes2011}.  However, fishers
establish favoured fishing grounds through an explore-exploit strategy
\citep{Rijnsdorp2011, Bailey2018} where they search for areas with high catches
and then use experience to return to areas where they've experienced high catch
in the past.  This leads to an inherently biased sampling where target species
are over-represented in the catch as fishers exploit areas of high abundance.
There is a need to understand the influence of these biases on any spatial
management measures which are implemented based on inference from commercial
landings or catch data. \\

To understand the effect of spatiotemporal aggregation of data and fishery
targeting on our perception of spatial abundance of different fish populations
we ask two fundamental questions regarding inference derived from observational
data:

\begin{enumerate}
	\item Do different source of sampling-derived fisheries data
		reflects the underlying community structure? 	
	\item How does data aggregation and data source impact on the success
		of spatial fisheries management measures?
\end{enumerate}
